Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-14 paper.tex
Add critical twist citation

It is evident from the kinetic energy profile that the flute instability
develops much earlier than in the $\eta=10^{-4}$ cases and grows at an
increased rate of $\gamma = 1.06$ (Figure~\ref{fig:kink_ke_log-3}). The kink
instability grows at a rate of $\lambda \approx 0.15$, much slower than that
observed in the $\eta=10^{-4}$ cases, and much lower than the flute
instability. \rev{The time period between $t\approx28$ and $t\approx32$ is
identified as the linear stage of the kink instability by investigating the
development shown in Figure~\ref{fig:swi-3_pressure_12}. This is consistent with the tube surpassing a critical twist of $2.59\pi$ between $t=28$ and $t=30$ (see~\citet{Torok2003}).} One key observation
is that, despite the early and disruptive growth of the flute instability, the
kink instability still generates the bulk of the kinetic energy
(Figure~\ref{fig:kink_ke-3}).

>>>>

It is evident from the kinetic energy profile that the flute instability
develops much earlier than in the $\eta=10^{-4}$ cases and grows at an
increased rate of $\gamma = 1.06$ (Figure~\ref{fig:kink_ke_log-3}). The kink
instability grows at a rate of $\lambda \approx 0.15$, much slower than that
observed in the $\eta=10^{-4}$ cases, and much lower than the flute
instability. \rev{The time period between $t\approx28$ and $t\approx32$ is
identified as the linear stage of the kink instability by investigating the
development shown in Figure~\ref{fig:swi-3_pressure_12}. This is broadly consistent with the tube surpassing a critical twist of $2.59\pi$~\citep{hood1981,torok2003} between $t=30$ and $t=35$.} One key observation
is that, despite the early and disruptive growth of the flute instability, the
kink instability still generates the bulk of the kinetic energy
(Figure~\ref{fig:kink_ke-3}).
